% Selina help with this file
\begin{enumerate}
\item \href{https://www.linkedin.com/in/maxine-rockoff-394b114/}{Maxine Rockoff}(University of Pennsylvania, 1964), currently an adjunct associate research scientist at Columbia University.
\item \href{http://euclid.colorado.edu/~gustafs/}{Karl Gustafson}(University of Pennsylvania, 1965), currently a professor of mathematics at University of Colorado Boulder.
\item \href{https://cs.uwaterloo.ca/~rbsimpso/RBScv.pdf}{Richard Bruce Simpson}(University of Maryland, 1966), used to be a professor of computer science at uniersity of Waterloo, passed away in 2020.
\item \href{https://ep.jhu.edu/faculty/james-kuttler/}{James Kuttler}(University of Maryland, 1967), currently an instructor in JHU Whiting School of Engineering.
\item \href{https://en.wikipedia.org/wiki/Stephen_Hilbert}{Stephan Hilbert}(University of Maryland, 1969), used to be a professor of mathematics at Ithaca College.
\item \href{https://sites.math.rutgers.edu/~falk/}{Richard Falk}(Cornell University, 1971), currently a professor of mathematics at Rutgers.
\item Thomas King(Cornell University, 1971).
\item \href{https://www.legacy.com/us/obituaries/knoxnews/name/steven-serbin-obituary?pid=120620923}{Steven Serbin}(Cornell University, 1971), used to be a professor of mathematics at University of Tennessee, passed away in 2008.
\item \href{http://www.math.buffalo.edu/mad/PEEPS/baker_gartha.html}{Garth Baker}(Cornell University, 1973), used to be a lecturer of mathematics at Bermuda College.
\item \href{https://services.math.duke.edu/~johnt/}{John Trangenstein}(Cornell University, 1975), currently a professor of mathematics at Duke University.
\item \href{https://www.math.tamu.edu/~joe.pasciak/}{Joseph E. Pasciak}(Cornell University, 1977), currently a professor of mathematics at Texas A\&M University.
\item \href{https://www.mn.uio.no/math/english/people/aca/rwinther/}{Ragnar Winther}(Cornell University, 1977), currently a professor of mathematics at University of OSLO.
\item Peter Sammon(Cornell University, 1978).
\item \href{https://www.uah.edu/science/departments/math/faculty-staff/mark-pekker}{Mark J. Pekker}(Cornell University, 1982), currently a professor of mathematics at The University of Alabama in Huntsville.
\item \href{https://www.personal.psu.edu/jxx1/}{Jinchao Xu}(Cornell University, 1989), currently a professor of mathematics at Pennsylvania State University. 
\item Ping Lee(Cornell University, 1990).
\item Mark Hanisch(Cornell University, 1991).
\item \href{https://www.bgsu.edu/arts-and-sciences/mathematics-and-statistics/faculty-and-staff/tong-sun.html}{Tong Sun}(Texas A\&M, 1997), currently a professor of mathematics at Bowling Green State University.
\item \href{http://web.pdx.edu/~gjay/}{Jay Gopalakrishnan}(Texas A\&M, 1999), currently a professor of mathematics at Portland State University.
\item \href{http://www.math.udel.edu/~bacuta/}{Constantin Bacuta}(Texas A\&M, 2000), currently a professor of mathematics at University of Delaware.
\item \href{https://people.llnl.gov/kolev1}{Tzanio Kolev}(Texas A\&M, 2004), currently a computational mathematician at Lawrence Livermore National Laboratory.
\item \href{https://scholar.google.com/citations?user=EeWTb_wAAAAJ&hl=en}{Dimitar Trenev} (Texas A\&M, 2009), currently working at ExxonMobil Corporate Strategic Research.
\end{enumerate}
